Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
Adding a reference to the name of NodIO-W2 and erasing the explanation of number of PUTs, because it was already explained

The results reported above indicated that we should look for a way of
increasing the time users spend on the page. This led us to create an
architecture that uses Web Workers, which is described in
\cite{2016arXiv160101607Manom}; web workers work in the background even if
the web page is not in focus. A few improvements were also tested,
basically using a random population and restarting the web worker when
the solution was found.

@@

However, it is interesting to note why this is so, and the first hint
is the inter-experiment correlation between the number of IPs in
successive experiments. While before it was an unremarkable 10\%, it is
now more than 43\%, making the number of IPs in contiguous experiments
highly correlated. The main reason for this is the setup in {\sf
  NodIO-W$^2$}, which restarts an island after a solution has been
found and also that it keeps running even if the tab is not on the
foreground. This means that volunteers can leave the experiment
running for as long as they want and they will be contributing 
experiment after experiment, unlike the previous version, where they
stopped contributing after one solution was found. This is also
reflected in the number of PUTs, which is the number of generations
divided by 100; more than 50\% of the volunteers run the experiment for more than
4000 generations. All things considered, this means than there are
%Mario: many more more threads {\em simultaneously} running?
many more computers {\em simultaneously} running, leading to this
almost 5-fold increase in running time.

>>>>

The results reported above indicated that we should look for a way of
increasing the time users spend on the page. This led us to create an
architecture that uses Web Workers, which is described in
\cite{2016arXiv160101607Manom} and is called {\sf
  NodIO-W$^2$}; web workers work in the background even if
the web page is not in focus. A few improvements were also tested,
basically using a random population and restarting the web worker when
the solution was found.

@@

However, it is interesting to note why this is so, and the first hint
is the inter-experiment correlation between the number of IPs in
successive experiments. While before it was an unremarkable 10\%, it is
now more than 43\%, making the number of IPs in contiguous experiments
highly correlated. The main reason for this is the setup in {\sf
  NodIO-W$^2$}, which restarts an island after a solution has been
found and also that it keeps running even if the tab is not on the
foreground. This means that volunteers can leave the experiment
running for as long as they want and they will be contributing 
experiment after experiment, unlike the previous version, where they
stopped contributing after one solution was found. This is also
reflected in the number of PUTs, more than 50\% of the volunteers run the experiment for more than
4000 generations. All things considered, this means than there are
%Mario: many more more threads {\em simultaneously} running?
many more computers {\em simultaneously} running, leading to this
almost 5-fold increase in running time.
